Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2

### 2019-04-05 Thesis_Presentation/Presentazione/Presentazione.tex
update final thesis

\documentclass{beamer}
\usepackage[italian]{babel}
\usepackage[utf8]{inputenc}
\usepackage{default}
\usepackage{subcaption}
\usepackage{afterpage}
\usepackage{xcolor}
\usepackage{wrapfig}
\usepackage{caption}
\usepackage{bbm}
\usepackage{multimedia}

\newsavebox{\tempbox}
\usetheme{Padova}
\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\subtitle{\itshape Tesi di Laurea in Ingegneria dell'Automazione}
\author{Relatore: Prof. Angelo Cenedese\qquad\quad Laureando: Alberto Franco Correlatore: Prof. Vitor Santos}
\date{\vspace{0.4cm}15 Aprile 2019}

@@

	\begin{frame}{Design Adaptive MPC - parte 1} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.

@@

>>>>

\documentclass{beamer}
\usepackage[italian]{babel}
\usepackage[utf8]{inputenc}
\usepackage{default}
\usepackage{afterpage}
\usepackage{xcolor}
\usepackage{wrapfig}
\usepackage{caption,subcaption}
\usepackage[font={small,it}]{caption}
\usepackage{bbm}
%\usepackage{movie15}
%\usepackage{multimedia} 
%\newsavebox{\tempbox}
\usetheme{Padova}
\setbeamertemplate{caption}[numbered]
\title{Local Path Planning with Moving Obstacle Avoidance based on Adaptive MPC in ATLASCAR2}
\subtitle{\itshape Tesi di Laurea in Ingegneria dell'Automazione}
\author{Relatore: Prof. Angelo Cenedese\qquad\quad Laureando: Alberto Franco Correlatore: Prof. Vitor Santos}
\date{\vspace{0.4cm}15 Aprile 2019}

@@

	\begin{frame}{Formulazione del Problema} 
		\begin{columns}[onlytextwidth,T]
			\begin{column}[c]{0.35\textwidth}
				\begin{figure}
					\centering
					\includegraphics[width=
					\textwidth]{./images/car_model.pdf}
					\caption{Bicycle model.}
					\label{fig:car_model}
				\end{figure}
			\end{column}			
			\begin{column}[c]{0.6\textwidth}
					 Quality of \textbf{reconstruction} is related to the number
					of cameras from which the target is visible.
					We assume that such number is more likely to be
					higher if the field-of-views are overlapped.
			\end{column}
		\end{columns}
	\end{frame}

	\begin{frame}{Design Adaptive MPC - parte 1} % progettazione dell'algoritmo di anticollisione basato su un controllore MPC adattivo.
	\begin{columns}[onlytextwidth,T]
		\begin{column}[c]{0.72\textwidth}
		\begin{figure}[!h]
			\vspace{-2.3em}
			\centering
			\includegraphics[width=
			\textwidth]{./images/flowchart/flowchart.pdf}
			\captionsetup{singlelinecheck = false, format= hang, justification=raggedright,}
			\caption{Algoritmo decisionale.}
			\label{fig:flowchart}
		\end{figure}
		\end{column}	
		\vspace{-1.1em}		
		\begin{column}[c]{0.27\textwidth}
			Quality of \textbf{reconstruction} is related to the number
			of cameras from which the target is visible.
			We assume that such number is more likely to be
			higher if the field-of-views are overlapped.
		\end{column}
	\end{columns}
	\end{frame}

@@

	\begin{frame}{Risultati Simulativi}
		\begin{figure}								
		\href{run:./video/animation_one_obstacle_left_overtaking.avi}{\includegraphics[width=\textwidth]{./images/one_obstacle_right_overtaking/overtaking_pres.pdf}}
		\caption{\href{run:./video/animation_one_obstacle_left_overtaking.avi}{Sorpasso a sinistra di un ostacolo in movimento (animazione).}}
		\label{fig:un_ostacolo}
		\vspace{-1.5em}
		\end{figure}
		\begin{figure}
		\href{run:./video/animation_6_obstacles.avi}{\includegraphics[width=\textwidth]{./images/6_obstacles/6_obstacles_pres.pdf}}
		\caption{\href{run:./video/animation_6_obstacles.avi}{Sorpasso di 6 ostacoli in movimento (animazione).}}
		\label{fig:sei_ostacoli}
		\vspace{-1.5em}
		\end{figure}
		\begin{figure}
		\href{run:./video/animation_braking_overtaking.avi}{\includegraphics[width=\textwidth]{./images/three_obstacles_no_overtaking/braking_pres.pdf}}
		\caption{\href{./video/animation_braking_overtaking.avi}{Frenata e sorpasso di 3 ostacoli in movimento (animazione).}}
		\label{fig:frenata}
		\end{figure}
	\end{frame}

### 2019-04-05 Thesis_Presentation/Presentazione/images/flowchart/flowchart.tex
update final thesis

	\begin{tikzpicture}[font={\small\sffamily}, node distance = 3cm, auto, scale=0.75,every node/.style={transform shape}]
	% Place nodes
	\node [decision] (detection) {Obstacle 
		detected?}; 
	\node [cloud,left of=detection] (start) {Start};
	\node [decision,below of=detection] (multiObstacles) {Multiple Obstacles detected?};
	\node [block,right of=detection] (reference) {Follow Path: stick to the lane};
	\node [block,left of=multiObstacles] (distance) {Obtain distance to closest obstacle};
	\node [block,right of=multiObstacles] (distances) {Obtain distance between the obstacles};
	\node [decision,below of=distances](space) {Free Space for Overtaking?};
	\node [block,right of=space,node distance=3.3cm](braking){Braking/ Ostacle Velocity};
	\node [block,below of=space](free){Overtaking on free lane};
	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {Left w.r.t vehicle?};
	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Right Overtaking};     
	\node [block, right of=decisionOvertaking] (leftOver) {Left Overtaking};

	%  \node [block] (init) {initialize model};
	% \node [cloud, left of=init] (expert) {expert};
	% \node [cloud, right of=init] (system) {system};
	% \node [block, below of=init] (identify) {identify candidate models};
	%    \node [block, below of=identify] (evaluate) {evaluate candidate models};
	%   \node [block, left of=evaluate, node distance=3cm] (update) {update model};
	%  \node [decision, below of=evaluate] (decide) {is best candidate better?};
	% \node [block, below of=decide, node distance=3cm] (stop) {stop};
	% Draw edges
	\path [line] (start) -- (detection);
	\path [line] (detection) -- node {yes} (multiObstacles);
	\path [line] (detection) -- node {no} (reference);
	\path [line] (multiObstacles) -- node {no} (distance);
	\path [line] (multiObstacles) -- node {yes} (distances);
	\path [line] (distances)--(space);
	\path [line] (space) -- node{no}(braking);
	\path [line] (space) -- node{yes} (free);
	\path [line] (braking) |- (distances);
	\path [line] (distance) -- (decisionOvertaking);
	\path [line] (decisionOvertaking) -- node {no}(leftOver);
	\path [line] (decisionOvertaking) -- node{yes} (rightOver);
	\end{tikzpicture}
\end{document}

>>>>

	\begin{tikzpicture}[font={\small\sffamily}, node distance = 3cm, auto, scale=0.75,every node/.style={transform shape}]
	% Place nodes
	\node [decision] (detection) {Rilevato Ostacolo?}; 
	\node [cloud,left of=detection] (start) {Inizio};
	\node [decision,below of=detection] (multiObstacles) {Rilevati Multipli Ostacoli?};
	\node [block,right of=detection] (reference) {Seguire il percorso: attenersi alla corsia};
	\node [block,left of=multiObstacles] (distance) {Calcola la distanza da quello più vicino};
	\node [block,right of=multiObstacles] (distances) {Calcola la distanza tra gli ostacoli};
	\node [decision,below of=distances](space) {Spazio libero per sorpassare?};
	\node [block,right of=space,node distance=3.3cm](braking){Frenata/ Velocità Ostacolo};
	\node [block,below of=space](free){Sorpasso nella corsia libera};
	\node [decision,below of=distance,node distance=2.5cm] (decisionOvertaking) {A sinistra rispetto al veicolo?};
	\node [block, below of=decisionOvertaking,node distance=2.5cm] (rightOver) {Sorpasso a Destra};     
	\node [block, right of=decisionOvertaking] (leftOver) {Sorpasso a Sinistra};

	%  \node [block] (init) {initialize model};
	% \node [cloud, left of=init] (expert) {expert};
	% \node [cloud, right of=init] (system) {system};
	% \node [block, below of=init] (identify) {identify candidate models};
	%    \node [block, below of=identify] (evaluate) {evaluate candidate models};
	%   \node [block, left of=evaluate, node distance=3cm] (update) {update model};
	%  \node [decision, below of=evaluate] (decide) {is best candidate better?};
	% \node [block, below of=decide, node distance=3cm] (stop) {stop};
	% Draw edges
	\path [line] (start) -- (detection);
	\path [line] (detection) -- node {si} (multiObstacles);
	\path [line] (detection) -- node {no} (reference);
	\path [line] (multiObstacles) -- node {no} (distance);
	\path [line] (multiObstacles) -- node {si} (distances);
	\path [line] (distances)--(space);
	\path [line] (space) -- node{no}(braking);
	\path [line] (space) -- node{si} (free);
	\path [line] (braking) |- (distances);
	\path [line] (distance) -- (decisionOvertaking);
	\path [line] (decisionOvertaking) -- node {no}(leftOver);
	\path [line] (decisionOvertaking) -- node{si} (rightOver);
	\end{tikzpicture}
\end{document}
